Basics of Hardware Cache Optimization

### 2017-05-26 tex/types.tex
Use varioref in addition to hyperref and cleveref
https://ctan.org/pkg/varioref
Minor update

Up to 32 KiB, each access takes almost exactly 3 cycles.%
\footnote{The numerical results are shown in \cref{tab:access-times}.}
This is the \gls{l1d} access \alts{time, latency}.  At 32 KiB (the size of the \gls{l1d})
the time increases to about 3.4 cycles.  This is not surprising since the cache is shared
with other processes and the operating system, so some of our data gets evicted.  The
first dramatic increase happens at 64 KiB followed by smaller increases at 128 and 256
KiB.  I suspect we are seeing a mixture of \gls{l2} and \gls{l1d} accesses, with less and
less \gls{l1d} hits and an \gls{l2} access time of around 25 cycles.

@@

>>>>

Up to 32 KiB, each access takes almost exactly 3 cycles.%
\footnote{The numerical results are shown in \vref{tab:access-times}.}
This is the \gls{l1d} access \alts{time, latency}.  At 32 KiB (the size of the \gls{l1d})
the time increases to about 3.4 cycles.  This is not surprising since the cache is shared
with other processes and the operating system, so some of our data gets evicted.  The
first dramatic increase happens at 64 KiB followed by smaller increases at 128 and 256
KiB.  I suspect we are seeing a mixture of \gls{l2} and \gls{l1d} accesses, with less and
less \gls{l1d} hits and an \gls{l2} access time of around 25 cycles.

@@

\Cref{sec:prefetch} will explain the reason for going through the trouble of conducting
random accesses instead of just reading the array sequentially for this measurement.
% We will see why this measurement was conducted with random instead of sequential
% accesses in \cref{sec:prefetch}.
